Asimilación de distintas observaciones

### 2021-07-27 analysis/chapters/experimento_20181122.Rmd
Old stuff

experiments <- c("E4", "E5", "E6", "E7", "E8")
#Color blind friendly but E4 y E7 parecidos en Desaturated
colores_exp <- c(E4 = "#0077BB", E5 = "#88CCEE", E6 = "#EE7733", E7 = "#CC3311") 
# colores_exp <- c(E4 = "#225555", E5 = "#CCBB44", E6 = "#CC6677", E7 = "#882255")
satinfo <- fread(here("analysis", "data", "derived_data", "satinfo.txt")) %>% 
  setnames(c("!sensor/instr/sat", "chan"), c("sensor", "channel"))
derived_data <- "/home/paola.corrales/datosmunin/EXP/derived_data/"

@@

files <- Sys.glob("/home/paola.corrales/datosmunin/EXP/derived_data/perfiles_mse*")

@@

perfiles_mse %>% 
  .[variable == "T"] %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = mse, fill = stat(level))) +
  scale_fill_viridis_c(option = "A", direction = -1,
                       name = NULL, super = ScaleDiscretised,
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  labs(subtitle = "Temperature MSE (K^2)",
       x = NULL,
       y = "Pressure level") +
  scale_y_level(name = "Pressure level", breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_x_datetime(expand = c(0,0), date_labels = "%HZ \n %b-%d", date_breaks = "24 hours") +
  facet_wrap(~exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                               E6 = "SATWND", E7 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

@@

The differences between RAD and SATWND and therefore the impact of the radiances have opposite sign to the impact of the observations from automatic stations but with smaller magnituded in low levels. A positive difference can also be observed between 850 and 600 hPa. 
```{r Q-mse, eval=FALSE, fig.cap="MSE", include=FALSE}

perfiles_mse %>% 
  .[variable == "QVAPOR"] %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = mse*1000000, fill = stat(level))) +
  scale_fill_viridis_c(option = "A", direction = -1,
                       name = NULL, super = ScaleDiscretised,
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  labs(subtitle = "Specific humidity MSE (g/Kg^2)",
       x = NULL,
       y = "Pressure level") +
  scale_y_level(name = "Pressure level", breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_x_datetime(expand = c(0,0), date_labels = "%HZ \n %b-%d", date_breaks = "24 hours") +
  facet_wrap(~exp, labeller = labeller(exp = c(E4 = "CONV", E5 = "AUT", 
                                               E6 = "SATWND", E7 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

@@

@@

@@

>>>>

experiments <- c("E4", "E5", "E6", "E7", "E8")
#Color blind friendly but E4 y E7 parecidos en Desaturated
colores_exp <- c(E4 = "#0077BB", E5 = "#88CCEE", E6 = "#EE7733", E7 = "#CC3311") 
# colores_exp <- c(E4 = "#225555", E5 = "#CCBB44", E6 = "#CC6677", E7 = "#882255")
satinfo <- fread(here("analysis", "data", "derived_data", "satinfo.txt")) %>% 
  setnames(c("!sensor/instr/sat", "chan"), c("sensor", "channel"))
derived_data <- "/home/paola.corrales/datosmunin3/EXP/derived_data/"

@@

files <- Sys.glob("/home/paola.corrales/datosmunin3/EXP/derived_data/perfiles_rmsd*")

@@

perfiles_mse %>% 
  .[variable == "T"] %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = rmsd, fill = stat(level))) +
  scale_fill_viridis_c(option = "A", direction = -1,
                       name = NULL, super = ScaleDiscretised,
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  labs(subtitle = "Temperature RMSD (K)",
       x = NULL,
       y = "Pressure level") +
  scale_y_level(name = "Pressure level", breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_x_datetime(expand = c(0,0), date_labels = "%HZ \n %b-%d", date_breaks = "24 hours") +
  facet_wrap(~exp, labeller = labeller(exp = c(E2 = "CONV", E5 = "AUT", 
                                               E6 = "SATWND", E8 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

@@

The differences between RAD and SATWND and therefore the impact of the radiances have opposite sign to the impact of the observations from automatic stations but with smaller magnituded in low levels. A positive difference can also be observed between 850 and 600 hPa.

```{r Q-mse, eval=FALSE, fig.cap="MSE", include=FALSE}

perfiles_mse %>% 
  .[variable == "QVAPOR"] %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = rmsd, fill = stat(level))) +
  scale_fill_viridis_c(option = "A", direction = -1,
                       name = NULL, super = ScaleDiscretised,
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  labs(subtitle = "Specific humidity RMSD (g/Kg)",
       x = NULL,
       y = "Pressure level") +
  scale_y_level(name = "Pressure level", breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_x_datetime(expand = c(0,0), date_labels = "%HZ \n %b-%d", date_breaks = "24 hours") +
  facet_wrap(~exp, labeller = labeller(exp = c(E2 = "CONV", E5 = "AUT", 
                                               E6 = "SATWND", E8 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

@@

```{r U-mse, eval=FALSE, fig.cap="MSE", include=FALSE}

perfiles_mse %>% 
  .[variable == "U"] %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = rmsd, fill = stat(level))) +
  scale_fill_viridis_c(option = "A", direction = -1,
                       name = NULL, super = ScaleDiscretised,
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  labs(subtitle = "U RMSD (m/s)",
       x = NULL,
       y = "Pressure level") +
  scale_y_level(name = "Pressure level", breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_x_datetime(expand = c(0,0), date_labels = "%HZ \n %b-%d", date_breaks = "24 hours") +
  facet_wrap(~exp, labeller = labeller(exp = c(E2 = "CONV", E5 = "AUT", 
                                               E6 = "SATWND", E8 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

@@

```{r V-mse, eval=FALSE, fig.cap="MSE", include=FALSE}

perfiles_mse %>% 
  .[variable == "V"] %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = rmsd, fill = stat(level))) +
  scale_fill_viridis_c(option = "A", direction = -1,
                       name = NULL, super = ScaleDiscretised,
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  labs(subtitle = "V RMSD (m/s)",
       x = NULL,
       y = "Pressure level") +
  scale_y_level(name = "Pressure level", breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_x_datetime(expand = c(0,0), date_labels = "%HZ \n %b-%d", date_breaks = "24 hours") +
  facet_wrap(~exp, labeller = labeller(exp = c(E2 = "CONV", E5 = "AUT", 
                                               E6 = "SATWND", E8 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))
```

@@

```{r}
files <- Sys.glob(paste0(derived_data, "mucape/mcape_ana_E[2,5,6,8]_20181122*.nc"))

dates <- c("20181122000000", "20181122060000", 
           "20181122120000", "20181122180000",
           "20181123000000")

fcsts <- expand_grid(fcsts = dates,
                     exp = c("E2", "E5", "E6", "E8"))

cor <- lapply(seq_len(nrow(fcsts)), function(f) {

  tmp <- ReadNetCDF(paste0(derived_data, "/u_", fcsts[f, 1], "_", fcsts[f, 2], ".nc"), vars = c(u = "uvmet")) %>% 
    .[, v := ReadNetCDF(paste0(derived_data, "/v_", fcsts[f, 1], "_", fcsts[f, 2], ".nc"), vars = c(v = "uvmet"), out = "vector")] %>% 
    .[, q := ReadNetCDF(paste0(derived_data, "/q_", fcsts[f, 1], "_", fcsts[f, 2], ".nc"), vars = c(q = "QVAPOR"), out = "vector")] %>% 
    .[, theta := ReadNetCDF(paste0(derived_data, "/theta_", fcsts[f, 1], "_", fcsts[f, 2], ".nc"), vars = c(th = "theta"), out = "vector")] %>%
    .[, date :=  ymd_hms(fcsts[f, 1])] %>% 
    .[, exp := fcsts[f, 2]] %>%  
    .[]
}) %>% 
  rbindlist() %>% 
.[bottom_top %in% c(1, 16)] %>% 
  dcast(date + exp + south_north + west_east ~ bottom_top, value.var = c("u", "v")) %>% 
  .[, cortante := Mag(u_16 - u_1, v_16 - v_1)] %>% 
  .[, ":="(u_2 = NULL, 
           u_10 = NULL,
           v_2 = NULL,
           v_10 = NULL)]
```
